Installation

### 2024-07-15 nbs/guides/installation.qmd
docs(guides): add note on dependency versions
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

>>>>

::: {#nte-versions .callout-important collapse=true title="Installation or usage errors and version constraints"}
If you have any issue with errors being raised during installation or usage
please check carefully that the version your package manager has installed is equivalent
to or newer than the one listed in the
[poetry.lock](https://github.com/pinellolab/pyrovelocity/blob/main/poetry.lock)
file in the repository.
We aim to support all latest stable versions of third-party dependencies
by lifting lower bounds on version constraints in the 
[pyproject.toml](https://github.com/pinellolab/pyrovelocity/blob/main/pyproject.toml) file.
This means that we generally do not support any older versions of dependencies
but consider any version more recent than the lower bound to be supported or a bug 
in pyrovelocity if attempting to use it produces an error.
Sometimes we are forced to delay support for a new version of a dependency
if it has been released released to PyPI but not yet to [conda-forge](https://conda-forge.org/packages/).
:::
